### 2012-12-04 inst/examples/policycosts/figure4.Rmd
working example of Figures 3 & 4
Still need to fully understand why asymmetric costs appear to be able to realize NPV0 policies, even though they cannot.

```{r}
i <- which(x_grid > K)[1]
dat <- 
lapply(policies, function(penalty) 
  sapply(penalty, function(c2_run)
    max(c2_run$penalty_free_V[i,]) 
  )
)
```

@@

``` {r npv-plot, dependson="quadcosts"}
npv0 <- max(dat$L1) # all have same max, at c2=0 
npv0
dat <- data.frame(c2=c2,dat)
dat <- melt(dat, id="c2")
ggplot(dat, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

@@

```{r apples_plot, dependson="quadcosts"}
ggplot(dat, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt <- data.table(dat)
index <- dt[,closest(.25, (npv0-value)/npv0), by=variable]
apples_index <- index$V1
names(apples_index) = index$variable
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

## Results

@@

@@

>>>>

```{r}
i <- which(x_grid > K)[1]
fees <- 
lapply(policies, function(penalty) 
  sapply(penalty, function(c2_run)
    max(c2_run$penalty_free_V[i,]) 
  )
)
```

@@

``` {r npv-plot, dependson="quadcosts"}
npv0 <- max(fees$L1) # all have same max, at c2=0 
npv0
fees <- data.frame(c2=c2,fees)
fees <- melt(fees, id="c2")
ggplot(fees, aes(c2, value, col=variable)) + geom_point() + geom_line()
````

@@

```{r apples_plot, dependson="quadcosts"}
ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
````

```{r apples, dependson="quadcosts"}
closest <- function(x, v){
  which.min(abs(v-x))
}
dt_npv <- data.table(fees)
index <- dt_npv[,closest(0.25, (npv0-value)/npv0), by=variable]
apples_index <- index$V1
names(apples_index) = index$variable
apples <- c2[index$V1]
names(apples) = index$variable
apples
````

@@

```{r}
v <- dt[,var(harvest), by="penalty_fn"]
var <- v$V1
names(var) <- v$penalty_fn
acor <- dt[,acf(harvest, plot=F)$acf[2], by="penalty_fn"]$V1
names(acor) <- names(var)
out <- rbind(var=var, a=acor)
out
```

@@

```{r}
source("fig4_helper_fun.R")
frac_lost <- seq(0,1, length=5)
out <- lapply(frac_lost, fig4, ls())
out <- melt(out)
colnames(out) = c("statistic", "penalty", "value", "index")
out <- cbind(out[1:3], fraction = frac_lost[out$index])
Figure4 <- ggplot(out) + geom_line(aes(fraction, value, col=penalty)) + facet_wrap(~statistic)
Figure4
````
